---
title: "MA_712_HW3"
output: html_notebook
---

by: Randy Cruz


```{r}
library(maxLik)
library(Zelig)
```


```{r}
data("turnout")
turnout
```


```{r}
library(ggplot2)
library(dplyr)

eduinc <- turnout%>%
  group_by(educate)%>%
  summarize(avincome=mean(income), n = n(), totalinc = sum(income))%>%
  mutate(percent = n/sum(n))
```

#Income In Relation to Education
Higher levels of education led to higher average of household Income.

```{r}
ggplot(eduinc)+
  geom_col(aes(x = educate, y = avincome), color= "Aqua Marine1", fill= "Orange")
```

#Income X Age Relationship
Ages 25 and 50 had higher reports of income. However, those who were 50+ displayed lower levels of income.

```{r}
ggplot(turnout)+
  geom_point(aes(x = age, y = income), color= "Orange") + geom_smooth(aes(x = age, y = income), color= "Aqua Marine1")
```

# Maximum Likelihood Estimation - Education X Age X Income
Overall, the analysis displays that age and education have a positive relationship with income. The MaxLik function adds to the analysis as it portrays for every 1 unit of education income goes up by (theta2).133. In addition, for every 1 unit of age, income increased by (theta3).017.



```{r, message=FALSE, warning=FALSE}
ols.lf2 <- function(param) {
  mu <- param[1]
  theta <- param[-1]
  y <- as.vector(turnout$income)
  x <- cbind(1, turnout$educate, turnout$age)
  sigma <- x%*%theta
  sum(dnorm(y, mu, sigma, log = TRUE))
}    

print(ols.lf2)

mle_ols2 <- maxLik(logLik = ols.lf2, start = c(mu = 1, theta1 = 1, theta2 = 1, theta3 = 1), method= "bfgs")
summary(mle_ols2)
```

